\bf Model Visualization Techniques for a Social Network Model

### 2017-10-30 paper-child.Rnw
add links to gifs and updated paper.

The first vizualization we present here is an animation of the simulated microsteps that form the transition steps of the CTMC from wave 1 to wave 2 of the small friendship network example shown in Figure~\ref{fig:alldataviz} when fitting model M1. Movies similar to this animation were used to visualize the changes of dynamic networks in \citet{dynnetviz}. When each ego node is selected in a microstep, it is emphasized in the animation, then the associated edge either appears or disappears. If there are no changes at a particular microstep, no changes are seen. Some frames of the animations are shown in Figure~\ref{fig:makinggif}, and the full movie can be viewed at INSERT LINK TO GIF.

@@

Using PCA on $\mathbf{A}^{cum}$ to order the rows and columns of the adjacency matrix visualization clearly shows the two distinct connected components in the first wave of the network, which are difficult to find in the arbitrarily ordered visualization. We also use the PCA seriated layout to fix the layout in the animation of one of the microstep process simulations. This animation, some frames of which are shown in Figure~\ref{fig:adjmatani} is very simple: a square appears or disappears in the animation as that edge appears or disappears in the microstep process. Through this animation, we can see edges appearing, and then later on disappearing. These in-between steps are not shown when we look at the network at our discrete observation points, so by viewing this animation we can gain a better understanding of the underlying dynamics of this model.

>>>>

The first vizualization we present here is an animation of the simulated microsteps that form the transition steps of the CTMC from wave 1 to wave 2 of the small friendship network example shown in Figure~\ref{fig:alldataviz} when fitting model M1. Movies similar to this animation were used to visualize the changes of dynamic networks in \citet{dynnetviz}. When each ego node is selected in a microstep, it is emphasized in the animation, then the associated edge either appears or disappears. If there are no changes at a particular microstep, no changes are seen. Some frames of the animations are shown in Figure~\ref{fig:makinggif}, and the full movie can be viewed at \url{https://vimeo.com/240089108}.

@@

Using PCA on $\mathbf{A}^{cum}$ to order the rows and columns of the adjacency matrix visualization clearly shows the two distinct connected components in the first wave of the network, which are difficult to find in the arbitrarily ordered visualization. We also use the PCA seriated layout to fix the layout in the animation of one of the microstep process simulations. This animation, some frames of which are shown in Figure~\ref{fig:adjmatani} is very simple: a square appears or disappears in the animation as that edge appears or disappears in the microstep process. Through this animation, we can see edges appearing, and then later on disappearing. These in-between steps are not shown when we look at the network at our discrete observation points, so by viewing this animation we can gain a better understanding of the underlying dynamics of this model. The full movie can be viewed at \url{https://vimeo.com/240092677}.
